Estimation of the road traffic sound levels based on the Semi-Supervised Non-Negative Matrix Factorization of Magnitude Spectrograms

### 2017-10-25 article/articleApplied.tex
Corrections ML

\section{Introduction}
With the introduction of the European Directive 2002/EC/49, cities over 100 000 inhabitants have to produce road traffic noise maps. It allows \ml{who ?}  to estimate the number of city dwellers exposed to high noise levels and to draw up action plans to reduce it as too long exposures to these noises can generate health problems \cite{who_burden_2017}. These maps are the result of a simulation process based on the estimation of the traffic density on the main roads and the use of sound propagation techniques. They express $L_ {DEN}$ and $L_N$, which are \textit{Day-Evening-Night} and \textit{Night} equivalent A-weighted sound levels respectively. However, these maps introduce lot of uncertainty generated by the numerical tools \cite{van_leeuwen_noise_2015}, by the different calculation methodologies used \cite{leroy_uncertainty_2010}\cite{garg_critical_2014} or even by the calculation procedure of the number of inhabitants exposed to noise \cite{king_implementation_2011}. In addition, the usual road traffic noise maps are static, aggregating the exposure on the two indicators $L_{DEN}$ and $L_N$, thus ignoring the sound levels evolution throughout the day. Since the creation of road traffic noise maps entails long data collection and calculation times, the use of acoustic measurements could facilitate their updating or even the generation of dynamic maps \cite{wei_dynamic_2016}. These measurements can be performed at fixed stations spread all over the cities \cite{Mioduszewski} \cite{mietlicki2012innovative}, which would lead to the availability of the long-term evolution of the traffic noise levels. It can also be performed with  mobile stations \cite{can_exploring_2012} \cite{manvell2004sadmam} covering a larger area with fewer sensors but also sparse time perdiods. The clustering between mobile and fixed measurements has been studied in \cite{can_measurement_2014}. \ml{je ne vois pas l'intéret de cette dernière phrase}

@@

If sensors networks could improve road traffic noise estimation compared with simulated maps, the issue of the correct estimation from  measurements of the traffic sound level is still unsolved \cite{Mioduszewski}. Indeed, the urban sound environment is a complex environment gathering lots of different sounds (car passages, voices, bird's whistles, car horn \dots) that can overlap. In consequence, the traffic sound level estimation based on measurements is not trivial task. \ml{parler ici de l'approche des espagnols. ref par email}

@@

We propose in this paper a method based on the Non-Negative Matrix Factorization technique to estimate the traffic sound level. To validate the approach, we consider a corpus of simulated (artifically created) scenes. The use of simulated sound scenes is necessary as it offers a full control on the design of the scenes and the knowledge of the exact contribution of the traffic component which would hardly be extracted from a recording of a urban scene.

The remaining of the paper is organized as follows. Section \ref{part:nmf} details the technical aspect of NMF. Section \ref{part:protocol} described on the experimental protocol setup. Then Section \ref{part:results} shows and discusses the results obtained during the parametric study.

\ml{faire une figure avec un diagrame de bloc et une section proposed approach avec des sub temps/frequence nmfsup nmfsemi}

\section{Non-negative Matrix Factorization}\label{part:nmf}
\subsection{Description of NMF}
Non-negative Matrix Factorization (NMF) is a matrix approximation method introduced by Lee and Seung, \cite{lee_learning_1999}, which can be used to approximate the spectrogram (obtained using a Short-Term Fourier Transform) of an audio file, $\mathbf{V}$, $\in \mathbb{R}^+_{F \times N}$ as :

@@

\begin{figure}[hbtp]
\centering
\includegraphics[width=0.9\linewidth]{../image/illustration_NMF.PNG}
\caption{Example of a simple NMF  for a musical content \cite{bertin_les_2009}}
\label{fig:example_NMF}
\end{figure}

@@

In order to vzlidate the usefulness of considering the NMF framewrok to estimate the road traffic noise level, one need to have a reference level. It can hardly de measured or even annotated from real life recordings. Thus,  simulated sound scenes are used to assess the performance of the propsed NMF. This offers a controlled framework to design specific sound environments in which all the traffic component is known. Then, the road traffic sound levels estimated with the method can be compared to the real ones, introduced within each simulated sound scene.

@@

A corpus is designed with the \textit{simScene} software\footnote{Open-source project available at: \url{https://bitbucket.org/mlagrange/simscene}}. \textit{simScene} \cite{rossignol_simscene:_2015} is a simulator that creates sound scenes in a .wav format by summing audio samples that come from an isolated sound database. This database is divided in two categories: $i)$ the \textit{event} category which are the brief sounds (from 1 to 20 seconds) that are considered as salient, $ii)$ the \textit{background} category includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. Inside each category, the sound samples are grouped in sound classes (\textit{bird, car, foot steps} \dots), each of them being composed of multiples samples (bird01.wav, bird02.wav \dots).

The software allows the user to control some parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may brings some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\

@@

A sound database has been built including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, birds, sweeping broom, car horn, car passages, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, train, tramway, truck and voice}) and 154 sound background samples divided in 9 sound classes (\textit{birds, construction site noise, crowd, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). The sound class \textit{car passages} comes from recordings of 4 cars made on the Ifsttar's runway on different speeds with multiple gear ratio. The other audio files have been found online (\textit{freesound.org}) and within the \textit{UrbanSound8k} database \cite{salamon_dataset_nodate}. This database enables creating realistic urban sound scenes from the road traffic point of view \cite{gloaguen_creation_2017}. A sound mixing corpus is composed of 6 sub-corpuses of 25 audio files each lasting 30 seconds. Each sub-corpus is characterized by a specific generic sound class that summed with traffic will make the estimation of the traffic level more difficult. The classes are : \textit{alert} (car horn, siren), \textit{animals} (barking dog , whistling birds), \textit{climate} (wind, rain), \textit{humans} (crowd noise and voice), \textit{mechanics} (different metallic and construction site noise) and \textit{transportation} (train, tramway and plane). In each file, traffic component is present as the sum of the background and event traffic sounds and is mixed with the sound classes. The sound classes that are not related to the traffic component are summed up as the \textit{interfering} sound class. To test different scenarios, each audio file is duplicated with the traffic sound level of the entire sound scene, $L_{p,traffic}$, fixed to a specific level according to the sound level of the \textit{interfering} class, $L_{p,interfering}$ following the relation (\ref{eq:tpr}).

\begin{equation}\label{eq:tpr}
TPR = L_{p,traffic}-L_{p,interfering}
\end{equation}

with the \textit{Traffic Interference Ratio} $TIR = \left[-12, -6, 0, 6, 12\right]$. When $TIR = -12$, the traffic component is then less present than when $TIR = 12$ where it is predominant on the \textit{perturbator} class. The 1 second equivalent sound pressure level, $p_{1s,traffic}$, is also calculated (figure \ref{fig:exampleScene}). Finally, the number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 TPR values).

@@

The experiment consists in estimating the traffic road sound level on the environmental sound corpus built using the simulation tool. NMF is used and compared to a baseli,e approach which consist in a frequency low-pass filter as road traffic is mainly composed of low frequencies, compared to main of the intefereing. this baseline has one parameter being the cut-off frequency $f_c$.

The spectrogram $\mathbf{V}$ is built with a window size $w = 2^{14}$ with a 75 $\%$ overlapping and a number of point $nfft = 2^{14}$. Therefore, the dimensions of $V$ are $F$ = 8192 and $N$ = 772.  Similarly, the frequency low-pass filter is applied on the spectrogram $\mathbf{V}$ and on the dictionary $\mathbf{W}$ ( renamed $\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$ respectively). This to focus the NMF estimation of the signal on the frequencies where the traffic components are most present. The figure \ref{fig:block_diagram_protocol} summarizes the different steps of the process depending on the chosen method, which consist of 3 steps:

\begin{itemize}
\item the dictionary building for NMF,
\item the estimation of the traffic sound level according the chosen method (NMF or frequency low-pass filter),
\item the calculation of the error between the exact and the estimated sound levels.\\
\end{itemize}

\begin{figure*}[!t]
\centering
	\begin{minipage}[t]{.48\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../image/bloc_diagram_filtrage_EN.pdf}
	\end{minipage}
	\begin{minipage}[t]{.48\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{../image/bloc_diagram_NMF_EN.pdf}
	\end{minipage}
	\caption{Block diagrams summed up the different step of the precess. On top, for the frequency low-pass filter, on bottom, for NMF.}
	\label{fig:block_diagram_protocol}
\end{figure*}

\subsubsection{Dictionary building}

The dictionary is built from a sound database dedicated specifically to this task. It is composed of 53 audio files of passing cars. First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 75 $\%$ overlap, $nfft$). Then a temporal rectangular window \ml{pourquoi pas de fenetrage ?} is applied without overlapping on the spectrogram in order to consider several spectrum for each audio file. The size of the window is set up at 0.5 and 1 second. In each window, the root mean square value is calculated on each frequency bin to reduce the different spectrum in one spectra.  An example that illustrates the process can be found on figure \ref{fig:dictionaryExtraction} in the ease of a large window of 4 seconds.

\begin{figure}[!t]
\centering
	\begin{minipage}[t]{.24\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../image/extractionDictionary1Example.pdf}
	\end{minipage}
	\begin{minipage}[t]{.24\textwidth}
		\centering
		\includegraphics[width=\linewidth]{../image/extractionDictionary2Example.pdf}
	\end{minipage}
	\caption{Example of the computation of the spectrum with a 1 second window. On left, the original spectrogram with the temporal window, on the left, the 4 spectrum obtained (dB scale)}
	\label{fig:dictionaryExtraction}
\end{figure}

Since the number of elements given by porcessing all the sound database does not respect the constraint imposed about the dimension of NMF ($F \times K + K \times N < F \times N$), a $K$-medoid clustering is applied to reduce the number of spectrum to $K = \left[ 25, 50, 100 \right]$. A special case is added where the root mean square of \textit{all} the spectrogram is applied. One spectra is then generated by audio file. \ml{pas clair}
Each element is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ is the $\ell-1$ norm. Table \ref{tab:dictionary_factors} summarizes the parameters and their related values.

\begin{table}[h]
\centering
\begin{tabular}{cccc}
$K$ & 25  & 50 & 100 \\ \hline
\begin{tabular}[c]{@{}c@{}}\textbf{temporal} \\ \textbf{window (s)}\end{tabular} & 0.5 & 1  & \textit{all}
\end{tabular}
\caption{Summary of the dictionary parameters}
\label{tab:dictionary_factors}
\end{table}

\subsubsection{Estimation of the traffic sound level}
The traffic sound level is estimated according to the choice of the estimator (a frequency low-pass filter or NMF). These methods are applied on the totality of the corpus (\textit{alert} (al), \textit{animals} (an), \textit{humans} (hu), \textit{climate} (cl), \textit{mechanics} (me), \textit{transportation} (tr)), for all the cut-off frequencies $f_c$ ([500 1k 2k 5k 10k 20k] Hz) and for 5 $TPR$ ([-12 -6 0 6 12] dB).

\paragraph{Frequency low-pass filter}\mbox{} \\
The first estimator to determine the traffic sound level is a basic frequency low-pass filter which depend only on the cut-off frequencies $f_c$.

\paragraph{NMF}\mbox{} \\
The second estimator is supervised and semi-supervised NMF (see part \ref{part:nmf}). The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed on two different formats: with a linear frequency scale ($\Delta f \approx 2.8$ Hz) and with third octave bands (27 bands). Theses two methods are considered to compare a fine grain approach (the linear scale) with a coarser one (the third octave bands) as it reduces the number of frequency bins and allows to reduces the number of bands in the high frequencies where the traffic component is less present. NMF inference is performed for 400 iterations which is sufficiently enough to get a stabilized reconstruction. Furthermore, in the case of the linear frequency scale, $\mathbf{V}$ and $\mathbf{W}$ are filtered at the frequencies $f_c$ in order to focused the reconstruction of the signal of the low frequency bins. As a consequence, if NMF is performed with filtered elements ($\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$) to determine $\mathbf{H}_{f_c}$, the traffic signal reconstruction is done with the original dictionary $\mathbf{W}$, as

@@

For the third octave frequency scale, only the case $f_c = 20$ kHz is applied.
During the iteration process, the estimated equivalent traffic sound level in dB of the entire scene, $\tilde{L}_{p,traffic}$, is calculated as well as the 1 second equivalent sound pressure level, $\tilde{p}_{1s,traffic}$. Table \ref{tab:estimation_factors} summarizes the parameters and their related values.

\begin{table*}[]
\centering
\begin{tabular}{lcccccc}
$\mathbf{f_c}$ (kHz) & 0.5 & 1 & 2 & 5 & 10 & 20 \\ \hline
$\mathbf{TPR}$ (dB) & -12 & -6 & 0 & 6 & 12 &  \\ \hline
\textbf{sub-classes} & alert & animals & climate & humans & transportation & mechanics \\ \hline
\textbf{method} & \multicolumn{2}{c}{filter} & \multicolumn{2}{c}{supervised NMF} & \multicolumn{2}{c}{semi-supervised NMF} \\ \hline
$\mathbf{\beta}$ & \multicolumn{3}{c}{1} & \multicolumn{3}{c}{2} \\ \hline
\begin{tabular}[c]{@{}c@{}}\textbf{frequency} \\ \textbf{scale}\end{tabular} & \multicolumn{3}{c}{linear} & \multicolumn{3}{c}{third octave}
\end{tabular}
\caption{Summary of the different parameters and their values for the estimation of the traffic sound level}
\label{tab:estimation_factors}
\end{table*}

\subsubsection{Metrics}
The performances of the two estimators of the road traffic sound level are assessed through the calculation of two metrics.

@@

In all, according the table \ref{tab:dictionary_factors} and \ref{tab:estimation_factors}, 6848 settings are performed between the different dictionary $\mathbf{W}$ and the multiple parameters of the estimation step.

@@

\begin{table}[h]
\centering
\begin{tabular}{llll}
$f_c$ (Hz) & $MAE$ (dB) & $nRMSE$  \\ \hline
 500 & \textbf{\textcolor{red}{5.66 $\pm$6.59}} & \textbf{\textcolor{red}{1.48 $\pm$1.10}} \\
 1000 & \textbf{6.31 $\pm$7.64} & \textbf{1.52 $\pm$1.34} \\
 2000 & \textbf{6.65 $\pm$8.24} & \textbf{1.57 $\pm$1.54} \\
 5000 & \textbf{7.42 $\pm$8.90} & 1.82 $\pm$1.65 \\
10000 & \textbf{7.55 $\pm$9.00} & 1.89 $\pm$1.70 \\
20000 & \textbf{7.59 $\pm$9.02} & 1.89 $\pm$1.72 \\
\end{tabular}
\caption{RMSE error for the low pass filter averaged on all the TPR and sub-classes}
\label{tab:results_filter}
\end{table}

According the table \ref{tab:results_filter}, the cut-off frequency at 500 Hz is the most efficient on all the TPR and all the sub-classes. The corresponding errors according to the sub-classes and the TPR are summarized in the figure \ref{fig:filterAmbiance}.\\

\begin{figure}[hbtp]
\centering
\includegraphics[width=\linewidth]{../image/AmbianceFilter.pdf}
\caption{Bar plot for the filter according to the sub-classes and the TPR at $f_c$ = 500 Hz cut-off frequency}
\label{fig:filterAmbiance}
\end{figure}

The error for all the sub-corpus is important for the low TPR (-12 and -6) due to the confusion between the \textit{perturbator} class and the \textit{traffic} class. The error is less for the \textit{alert} and \textit{humans} sub-corpus as it is composed of higher frequencies while, for other sub-classes, the error are far more important. For the higher \textit{TPR}, the traffic is more present and become dominating on the \textit{perturbator} class. The lower error, here, is due to the suppression of the traffic energy by the filter. Finally, the error for $f_c = 20$ kHz is equivalent to the one produced when the \textit{traffic} and the \textit{perturbator} classes are take into account together without distinction.

@@

\begin{table*}[t]
\centering
\begin{tabular}{lllllcc}
$K$ & \shortstack{temporal\\window (ms)} & $f_c$ (Hz) & domain & $\beta$ & $MAE$ (dB) & $nRMSE$ \\
\hline
 25 & 500 & spectra &  2000 & 1 & \textbf{6.18 $\pm$7.49} & \textbf{1.48 $\pm$1.20} \\
 25 & 500 & spectra &   500 & 2 & \textbf{\textcolor{red}{5.32 $\pm$6.28}} & \textbf{1.40 $\pm$0.93} \\
 25 & 0 & third octave & 20000 & 1 & \textbf{6.82 $\pm$8.16} & 1.60 $\pm$1.34\\
 25 & 500 & third octave & 20000 & 2 & \textbf{6.26 $\pm$7.69} & \textbf{\textcolor{red}{1.36 $\pm$1.19}} \\
\end{tabular}
\caption{RMSE error for supervised NMF averaged on all the TPR and sub-classes}
\label{tab:results_supervised}
\end{table*}

>>>>

\section{Introduction}
\subsection{Related work}
With the introduction of the European Directive 2002/EC/49, cities over 100 000 inhabitants have to produce road traffic noise maps. Theses maps allow to estimate the number of city dwellers exposed to high noise levels and to draw up action plans to reduce it as too long exposures to these noises can generate health problems \cite{who_burden_2017}. These maps are the result of a simulation process based on the estimation of the traffic density on the main roads and the use of sound propagation techniques. They express $L_ {DEN}$ and $L_N$, which are \textit{Day-Evening-Night} and \textit{Night} equivalent A-weighted sound levels respectively. However, these maps introduce lot of uncertainty generated by the numerical tools \cite{van_leeuwen_noise_2015}, by the different calculation methodologies used \cite{leroy_uncertainty_2010}\cite{garg_critical_2014} or even by the calculation procedure of the number of inhabitants exposed to noise \cite{king_implementation_2011}. In addition, the usual road traffic noise maps are static, aggregating the exposure on the two indicators $L_{DEN}$ and $L_N$, thus ignoring the sound levels evolution throughout the day. Since the creation of road traffic noise maps entails long data collection and calculation times, the use of acoustic measurements could facilitate their updating or even the generation of dynamic maps \cite{wei_dynamic_2016}. These measurements can be performed at fixed stations spread all over the cities \cite{Mioduszewski} \cite{mietlicki2012innovative}, which would lead to the availability of the long-term evolution of the traffic noise levels. It can also be performed with  mobile stations \cite{can_exploring_2012} \cite{manvell2004sadmam} covering a larger area with fewer sensors but also sparse time periods. %The clustering between mobile and fixed measurements has been studied in \cite{can_measurement_2014}. \ml{je ne vois pas l'intéret de cette dernière phrase}

\begin{figure*}
    \centering
    \subfigure[]{\label{fig:blocDiagramNMF}
    \includegraphics[width=.45\linewidth]{../image/bloc_diagram_NMF_EN.pdf}}
    \subfigure[]{\label{fig:blocDiagramFilter}	\includegraphics[width=.45\linewidth]{../image/bloc_diagram_filtrage_EN.pdf}}
    \caption{Block diagrams summed up the different step of the process for the frequency low-pass filter \ref{fig:blocDiagramFilter} and for NMF \ref{fig:blocDiagramNMF}.}
    \label{fig:blocDiagram}
\end{figure*}

@@

If sensors networks could improve road traffic noise estimation compared with simulated maps, the issue of the correct estimation from  measurements of the traffic sound level is still unsolved \cite{Mioduszewski}. Indeed, the urban sound environment is a complex environment gathering lots of different sounds (car passages, voices, bird's whistles, car horn \dots) that can overlap. Consequently, the traffic sound level estimation based on measurements is not trivial task. \ml{parler ici de l'approche des espagnols. ref par email}

@@

\subsection{Proposed approach}

We propose in this paper a method based on the Non-Negative Matrix Factorization (NMF) technique to estimate the global, $\tilde{L}_{p,traffic}$, and the 1-s equivalent, $\tilde{p}_{1s,traffic}$ sound level of the traffic through the supervised and the semi-supervised approaches. To validate this approach, we consider a corpus of simulated scenes artificially created with the simulator software \textit{simScene}. The use of simulated sound scenes is necessary as it offers a full control on the design of the scenes and the knowledge of the exact contribution of the traffic component which would hardly be extracted from a recording of an urban scene ($L_{p,traffic}$ and $p_{1s,traffic}$). Both the sound scene simulation and NMF require the creation of two sound databases (figure  \ref{fig:blocDiagramNMF}). In parallel, a baseline method built from a frequency low-pass filter is computed. This method considers that road traffic is mainly composed of low frequencies and therefore can be filtered by a low-pass filter at the cut-off frequency $f_c$ (figure \ref{fig:blocDiagramFilter}). The performance of the frequency low-pass filter and NMF are then compared with the calculation of two metrics (Mean Absolute Error, normalized Root Mean Square Error).

The remaining of the paper is organized as follows. Section \ref{part:nmf} details the technical aspect of NMF. Section \ref{part:protocol} described on the design of the environmental sound scene corpus and the experimental protocol setup. Then Section \ref{part:results} shows and discusses the results obtained during the parametric study.

%\ml{faire une figure avec un diagrame de bloc et une section proposed approach avec des sub temps/frequence nmfsup nmfsemi}

\section{Non-negative Matrix Factorization}\label{part:nmf}
\subsection{Description of NMF}
Non-negative Matrix Factorization is a matrix approximation method introduced by Lee and Seung, \cite{lee_learning_1999}, which can be used to approximate the spectrogram (obtained using a Short-Term Fourier Transform) of an audio file, $\mathbf{V}$, $\in \mathbb{R}^+_{F \times N}$ as :

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.9\linewidth]{../image/illustration_NMF.PNG}
\caption{Example of a simple NMF  for a musical content \cite{bertin_les_2009}}
\label{fig:example_NMF}
\end{figure}

@@

In order to validate the usefulness of considering NMF framework to estimate the road traffic noise level, one need to have a reference level. It can hardly be measured or even annotated from real life recordings. Thus,  simulated sound scenes are used to assess the performance of the proposed NMF. This offers a controlled framework to design specific sound environments in which all the traffic component is known. Then, the road traffic sound levels estimated with the method can be compared to the real ones, introduced within each simulated sound scene.

@@

A corpus is designed with the \textit{simScene} software\footnote{Open-source project available at: \url{https://bitbucket.org/mlagrange/simscene}}. \textit{simScene} \cite{rossignol_simscene:_2015} is a simulator that creates sound scenes in a .wav format by summing audio samples that come from an isolated sound database.

This database is divided in two categories: $i)$ the \textit{event} category which are the brief sounds (from 1 to 20 seconds) that are considered as salient including 245 sound event samples divided in 19 sound classes (\textit{ringing bell, birds, sweeping broom, car horn, car passages, hammer, drill, coughing, barking dog, rolling suitcase, closing door, plane, siren, footstep, storm, street noise, train, tramway, truck and voice}) and $ii)$ the \textit{background} category that includes all the sounds that are of long duration and whose acoustic properties do not vary with respect to time. 154 sound samples belong to this category divided in 9 sound classes (\textit{birds, construction site noise, crowd, park, rain, children playing in schoolyard, constant traffic noise, ventilation, wind}). The sound class \textit{car passages} comes from 60 recordings of 2 cars made on the Ifsttar's runway on different speeds with multiple gear ratio. The other audio files have been found online (\textit{freesound.org}) and within the \textit{UrbanSound8k} database \cite{salamon_dataset_nodate}. Each sound classes are composed of multiples samples (\textit{bird01.wav}, \textit{bird02.wav} \dots). 
The software allows the user to control some parameters (number of events of each class that appear in the mixture, elapsed time between each sample of a same class, presence of a fade in and a fade out \dots) completed with a standard deviation that may brings some random behavior between the scenes. Furthermore, an audio file of each sound class present in the scene can be generated that allows to know its exact contribution as well as a text file that summarizes the time presence of all the events.\\

@@

This database enables creating realistic urban sound scenes from the road traffic point of view \cite{gloaguen_creation_2017}. A sound mixing corpus is composed of 6 sub-corpus of 25 audio files each lasting 30 seconds. Each sub-corpus is characterized by a specific generic sound class that summed with traffic will make the estimation of the traffic level more difficult. The classes are : \textit{alert} (car horn, siren), \textit{animals} (barking dog , whistling birds), \textit{climate} (wind, rain), \textit{humans} (crowd noise and voice), \textit{mechanics} (different metallic and construction site noises) and \textit{transportation} (train, tramway and plane). In each file, traffic component is present as the sum of the background and event traffic sounds and is mixed with the sound classes. The sound classes that are not related to the traffic component are summed up as the \textit{interfering} sound class. To test different scenarios, each audio file is duplicated with the traffic sound level of the entire sound scene, $L_{p,traffic}$, fixed to a specific level according to the sound level of the \textit{interfering} class, $L_{p,interfering}$ following the relation (\ref{eq:tir}).

\begin{equation}\label{eq:tir}
TIR = L_{p,traffic}-L_{p,interfering}
\end{equation}

with the \textit{Traffic Interference Ratio} $TIR = \left[-12, -6, 0, 6, 12\right]$. When $TIR = -12$, the traffic component is then less present than when $TIR = 12$ where it is predominant on the \textit{interfering} class. The 1 second equivalent sound pressure level, $p_{1s,traffic}$, is also calculated (figure \ref{fig:exampleScene}). Finally, the number of scenes designed is 750 (6 sub-corpus $\times$ 25 scenes $\times$  5 TPR values).

@@

The experiment consists in estimating the traffic road sound level of the 6 environmental sound sub-corpus (\textit{alert} (al), \textit{animals} (an), \textit{humans} (hu), \textit{climate} (cl), \textit{mechanics} (me), \textit{transportation} (tr)) and for 5 $TIR$ ([-12 -6 0 6 12] dB). First, the spectrogram $\mathbf{V}$ of each sound scene is built with a window size $w = 2^{14}$ with a 75 $\%$ overlap and a number of point $nfft = 2^{14}$. Therefore, the dimensions of $V$ are $F$ = 8192 and $N$ = 772.

The first estimator to determine the traffic sound level is the basic frequency low-pass filter which depend only on the cut-off frequencies $f_c$ = [500 1k 2k 5k 10k 20k] Hz. The spectrograms $\mathbf{V}$ are filtered and the remaining energy is then considered as traffic component (equation \ref{eq:v_tr_filtered}).

\begin{equation}\label{eq:v_tr_filtered}
\mathbf{V}_{traffic} = \mathbf{V}_{f_c}
\end{equation}

The second estimator is NMF. Multiples parameters are involved here between the building of the dictionary and the performed NMF.

\subsubsection{Dictionary building}
The dictionary is built from a second sound database dedicated specifically to this task. It is composed of 53 audio files of passing cars. These records have been made on the Ifsttar's runway with the same conditions that the records made for the \textit{simScene} database but with two different cars (). First, for each audio file, its spectrogram is calculated with fixed parameters ($w$, 75 $\%$ overlap, $nfft$). Then time/frequency windows with $w_t \times F$ dimension are applied without overlapping on the spectrogram in order to consider several spectrum for each audio file. In each window, the root mean square value is calculated on each frequency bin to reduce the different spectrum in one spectra.

Since the number of elements given by processing all the sound database does not respect the constraint imposed about the dimension of NMF ($F \times K + K \times N < F \times N$), a $K$-medoid clustering is applied to reduce the number of spectrum to $K = \left[ 25, 50, 100 \right]$. A special case is added where the root mean square of \textit{all} the spectrogram is applied. One spectra is then generated by audio file. \ml{pas clair}
An example that illustrates the process can be found on figure \ref{fig:dictionaryExtraction} in the cases where $w_t$ = [1 \textit{all}].

\begin{figure}
    \centering
\begin{minipage}[t]{\linewidth}
    \subfigure[]{\label{fig:specW}
    \includegraphics[width=.45\linewidth]{../image/extractionDictionary1Example.pdf}}
    \subfigure[]{\label{fig:ElementW}
    \includegraphics[width=.45\linewidth]{../image/extractionDictionary2Example.pdf}}

    \caption{Example of the creation of the dictionary from the spectrogram of a bird's whistle sample (fig. \ref{fig:specW}). 2 time/frequency window :  with $w_t = 1$ s (fig. \ref{fig:ElementW} on left), 3 elements are composed while with $w_t = all$ (fig. \ref{fig:ElementW} on right), only one element is generated.}
    \label{fig:dictionaryExtraction}
    \end{minipage}
\end{figure}

Each $k$ element of $\mathbf{W}$ is normalized such as $\vert \vert \mathbf{W_k} \vert \vert = 1$ with $\vert \vert \bullet \vert\vert$ is the $\ell$-1 norm. Table \ref{tab:dictionary_factors} summarizes the parameters and their related values.

\begin{table}[h]
\centering
\begin{tabular}{cccc}
Parameter &  \multicolumn{3}{c}{value}\\ \hline
$K$ & 25  & 50 & 100 \\ \hline
$\mathbf{w_t}$& 0.5 & 1  & \textit{all}
\end{tabular}
\caption{Summary of the dictionary parameters}
\label{tab:dictionary_factors}
\end{table}

\subsubsection{Performed NMF}

NMF inference is performed for 400 iterations which is sufficiently enough to get a stabilized reconstruction. The spectrogram $\mathbf{V}$ and the dictionary $\mathbf{W}$ are expressed on two different formats: with a linear frequency scale ($\Delta f \approx 2.8$ Hz) and with third octave bands (29 bands). Theses two methods are considered to compare a fine grain approach (the linear scale) with a coarser one (the third octave bands) as it reduces the number of frequency bins and allows to reduces the number of bands in the high frequencies where the traffic component is less present.  Furthermore, in the case of the linear frequency scale, $\mathbf{V}$ and $\mathbf{W}$ are filtered at the frequencies $f_c$ in order to focused the reconstruction of the signal of the low frequency bins. As a consequence, if NMF is performed with filtered elements ($\mathbf{V}_{f_c}$ and $\mathbf{W}_{f_c}$) to determine $\mathbf{H}_{f_c}$. The traffic signal reconstruction is done with the original dictionary $\mathbf{W}$, as

@@

For the third octave frequency scale, only the case $f_c = 20$ kHz is applied.

\subsection{Metrics}
The performances of the two estimators of the road traffic sound level are assessed through the calculation of two metrics.

@@

In all, according the table \ref{tab:dictionary_factors} and \ref{tab:estimation_factors}, 6848 settings are performed between the different form of the dictionary $\mathbf{W}$ and the multiple parameters taken into account by NMF. Table \ref{tab:estimation_factors} summarizes the parameters and their related values.

\begin{table*}[]
\centering
\begin{tabular}{lcccccc}
Parameter &  \multicolumn{6}{c}{value}\\ \hline
$\mathbf{f_c}$ (kHz) & 0.5 & 1 & 2 & 5 & 10 & 20 \\ \hline
$\mathbf{TIR}$ (dB) & -12 & -6 & 0 & 6 & 12 &  \\ \hline
\textbf{sub-classes} & alert & animals & climate & humans & transportation & mechanics \\ \hline
\textbf{method} & \multicolumn{2}{c}{filter} & \multicolumn{2}{c}{supervised NMF} & \multicolumn{2}{c}{semi-supervised NMF} \\ \hline
$\mathbf{\beta}$ & \multicolumn{3}{c}{1} & \multicolumn{3}{c}{2} \\ \hline
\begin{tabular}[c]{@{}c@{}}\textbf{frequency} \\ \textbf{scale}\end{tabular} & \multicolumn{3}{c}{linear} & \multicolumn{3}{c}{third octave}
\end{tabular}
\caption{Summary of the different parameters and their values for the estimation of the traffic sound level}
\label{tab:estimation_factors}
\end{table*}

@@

\begin{table}[h]
\centering
\begin{tabular}{llll}
$f_c$ (Hz) & $MAE$ (dB) & $nRMSE$  \\ \hline
 500 & \textbf{\textcolor{red}{5.66 $\pm$6.59}} & \textbf{\textcolor{red}{1.48 $\pm$1.10}} \\
 1000 & \textbf{6.31 $\pm$7.64} & \textbf{1.52 $\pm$1.34} \\
 2000 & \textbf{6.65 $\pm$8.24} & \textbf{1.57 $\pm$1.54} \\
 5000 & \textbf{7.42 $\pm$8.90} & 1.82 $\pm$1.65 \\
10000 & \textbf{7.55 $\pm$9.00} & 1.89 $\pm$1.70 \\
20000 & \textbf{7.59 $\pm$9.02} & 1.89 $\pm$1.72 \\
\end{tabular}
\caption{RMSE error for the low pass filter averaged on all the TIR and sub-classes}
\label{tab:results_filter}
\end{table}

According the table \ref{tab:results_filter}, the cut-off frequency at 500 Hz is the most efficient on all the TIR and all the sub-classes. The corresponding errors according to the sub-classes and the TIR are summarized in the figure \ref{fig:filterAmbiance}.\\

\begin{figure}[hbtp]
\centering
\includegraphics[width=\linewidth]{../image/AmbianceFilter.pdf}
\caption{Bar plot for the filter according to the sub-classes and the TIR at $f_c$ = 500 Hz cut-off frequency}
\label{fig:filterAmbiance}
\end{figure}

The error for all the sub-corpus is important for the low TIR (-12 and -6) due to the confusion between the \textit{interfering} class and the \textit{traffic} class. The error is less for the \textit{alert} and \textit{humans} sub-corpus as it is composed of higher frequencies while, for other sub-classes, the error are far more important. For the higher \textit{TIR}, the traffic is more present and become dominating on the \textit{interfering} class. The lower error, here, is due to the suppression of the traffic energy by the filter. Finally, the error for $f_c = 20$ kHz is equivalent to the one produced when the \textit{traffic} and the \textit{interfering} classes are take into account together without distinction.

@@

\begin{table*}[t]
\centering
\begin{tabular}{lllllcc}
$K$ & \shortstack{temporal\\window (ms)} & domain & $f_c$ (Hz) & $\beta$ & $MAE$ (dB) & $nRMSE$ \\
\hline
 25 & 500 & spectra &  2000 & 1 & \textbf{6.18 $\pm$7.49} & \textbf{1.48 $\pm$1.20} \\
 25 & 500 & spectra &   500 & 2 & \textbf{\textcolor{red}{5.32 $\pm$6.28}} & \textbf{1.40 $\pm$0.93} \\
 25 & 0 & third octave & 20000 & 1 & \textbf{6.82 $\pm$8.16} & 1.60 $\pm$1.34\\
 25 & 500 & third octave & 20000 & 2 & \textbf{6.26 $\pm$7.69} & \textbf{\textcolor{red}{1.36 $\pm$1.19}} \\
\end{tabular}
\caption{RMSE error for supervised NMF averaged on all the TIR and sub-classes}
\label{tab:results_supervised}
\end{table*}
